### 2016-10-04 R/ITHIM.Rmd
Change to ITHIM.Rmd

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
library("ggplot2")
library("reshape2")
library("plyr")
library("dplyr")
library("cowplot")
library("grid")
library("scales")
```

@@

```{r California, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = phi, warning = FALSE, message = FALSE, echo = FALSE}

ITHIM.national <- updateITHIM(ITHIM.national, parName = "muNonTravel", 10)

@@

p <- ggplot( subset(foobar,ageClass != "ageClass1"), aes(ageClass,-delta.DALY/1e3) )
p + geom_bar(stat="identity", position = "dodge") + scale_x_discrete(name="", labels = c("5-14","15-29","30-44","45-59","60-69","70-79","80+")) + scale_y_continuous(name="DALYs Averted Nationwide (Thousands)") + facet_grid( Disease ~ State) + theme_bw() + coord_flip() # + theme(axis.text.x  = element_text(angle=90, vjust=0.5, size=8))
```

>>>>

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
library("ggplot2")
library("reshape2")
library("plyr")
library("dplyr")
library("cowplot")
library("grid")
library("scales")
library("ggthemes")
```

@@

```{r California, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = phi, warning = FALSE, message = FALSE, echo = FALSE}
ITHIM.national <- updateITHIM(ITHIM.national, parName = "muNonTravel", 10)

@@

p <- ggplot( subset(foobar,ageClass != "ageClass1"), aes(ageClass,-delta.DALY/1e3, fill = State) )

upper <- 10

p + geom_bar(stat="identity", position = "dodge") +
theme(axis.title=element_blank()) +
facet_grid( Disease ~ ., scales = "free") +
scale_y_continuous(breaks=seq(1, upper, 1), name="DALYs Averted Nationwide (Thousands)") +

#geom_hline(yintercept=seq(1, upper, 1), col="white", lwd=1) +
scale_x_discrete(name="", labels = c("5-14","15-29","30-44","45-59","60-69","70-79","80+")) +
theme_tufte(base_size=12, ticks=T) 
#

# + annotate("text", x = 3.5, y = 5, adj=1,  family="serif", label = c("Foo")) 
# + scale_y_continuous(name="DALYs Averted Nationwide (Thousands)") + facet_grid( Disease ~ State) + coord_flip() # + theme(axis.text.x  = element_text(angle=90, vjust=0.5, size=8))
```
